\chapter{Literature Survey}

This chapter consists of two parts.  In part one, give any necessary engineering and non-engineering backgrounds that you see important for the complete understanding of your project. These backgrounds include, but are not limited to, facts, theory, formulas, algorithms and techniques. In other words, any pivotal knowledge to your project should be given, discussed, and properly defined. In part two give a short literature review of the latest publications related to your project within past three years if applicable.  Specially in this chapter, avoid lengthy unrelated discussion. More important, copy-and-paste should never be used. You have to write everything with your style and wording.

In this space, before the first section, write an introductory paragraph to describe the topics and organization of the chapter

\section{Background on Topic 1}
Give this section a title related to the topic you cover and  then write the related information as explained above. 

\section{Background on Topic 2}
Similar to the previous section, give this section a title related to the topic you cover and  then write the related information as explained above. 
Just choose the most two important topics however you make sure to cover all necessary facts, theory, formulas, algorithms and techniques.

\section{Comparative Study of Previous Work}
In this section give a comparative, classified  short literature review of the latest publications the latest publications related to your project within past three years if applicable

\section{Implemented Approach}
Conclude this chapter by this section stating the approach chosen from those reviewed, but more important your justification why you chose this approach along with any modifications added to the approach.
Notice, you may be implementing several techniques however you must illustrate the general framework for your approach.
