\chapter{Development Platforms and Tools}
\section{Hardware Tools }
Personal computers running linux-based oberating systems.

\section{Software Tools}
\subsection{Programming Languages}
\subsubsection{Golang}
Go was created at Google to help programmers be more productive in an era of multicore, networked devices by including the following features: 
\begin{enumerate}[itemsep=1pt, topsep=5pt]
    \item Run-time efficiency (like C).
    \item Multiprocessing and high-performance networking.
    \item Readability and usability are two of the most important factors to consider (like Python).
\end{enumerate}
\textbf{Usage:} Main programming to build the core modules and daemons.

\subsubsection{Python}
Python is a high-level programming language that is interpreted and object-oriented. It's ideal for Rapid Application Development, as well as using as a scripting or glue language to link together existing components.
\\
\textbf{Usage:} To write testbed scripts

\subsubsection{Shell Scripting}
Shell scripting is a type of scripting that runs in the Unix/Linux shell.
It can condense long and repeated command sequences into a single, easy-to-understand script.
\\
\textbf{Usage:} For running repetitive commands with a single script.

\subsection{Libraries and Frameworks}
\subsubsection{Mininet}
Mininet builds a realistic virtual network on a single system, running actual kernel, switch, and application code.
\\
\textbf{Usage:} For testing our system with a variety of topologies.
\subsubsection{Socat}
Socat is a command-line utility for creating and transferring data across two bidirectional byte streams.
\\
\textbf{Usage:} For forwarding data from TCP to Unix sockets to make the user interface works on the browser, however the daemons are running inside containers without changing the interfacing.
\subsubsection{Nsenter}
It's a simple utility that lets you enter namespaces.
It can technically enter existing namespaces or start a new process in a different set of namespaces. 
\\
\textbf{Usage:} For Running the programs inside containers.
\subsubsection{React.js}
React is a JavaScript library for creating user interfaces that is fast and adaptable.
\\
\textbf{Usage:} Build both Command Center and Unit user interface (UI) as a web application.
\subsubsection{Electron.js}
Electron.js is a runtime framework for developing desktop applications.
\\
\textbf{Usage:} Build both Command Center and Unit user interface (UI) as a desktop application.
\subsection{Tools and Platforms}
\begin{itemize}
    \item Visual Studio Code: it is a free source-code editor with debugging support.
    \item GitHub: it is an online service that hosts Git repositories for software development and version control. 
\end{itemize}
